Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-27 sections/background.tex
lots of change to the paper text.

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}. The grey area shows the review process of the system which composed of four main steps. (1) an author creating a patch and submitting a set of new or modified files as a review request to Gerrit system. (2) reviewers examine the proposed code changes for defects or concerns. (3) reviewers provide comments to the author. The author creates a revised proposed change according to the comments then re-submits for review. Then, reviewers will examine the revised proposed change. If the revision is not approved, reviewers provide comments to fix and the process continues until (4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).

@@

According to this process, reviewers' comments are the most important factor in determining software quality. In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs. However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers) and frequently comments are superficial or do not clearly identify defects or relevant issues (e.g. design suggestions, coding styles, etc.) for the proposed change and are thus of questionable usefulness. For example a comment may relate to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!"). Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues. Our observations of the Qt project also correspond to this finding. We found some comments are superficial and unhelpful to the proposed changes. For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information. While the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

>>>>

An overview of MCR process based on Gerrit system is shown in Fig. \ref{fig:process}.
The grey area shows the review process of the system which composed of four main steps:
(1) an author creates a patch and submits a set of new or modified files as a review request to Gerrit system.
(2) reviewers examine the proposed code changes for defects or concerns.
(3) reviewers provide comments to the author. The author creates a revised proposed change according to the comments and re-submits for review. Then, reviewers will examine the revised proposed change. If the revision is not approved, reviewers provide comments to fix and the process continues until (4) reviewers can determine that a proposed change can be merged into the project (approved change) or should not be merged (reject the change).

@@

According to this process, reviewers' comments are the most important factor in determining software quality.
In particular, McIntosh et. al. \cite{Mcintosh} found that components which were reviewed without discussion are likely to contain bugs.
However, tools supporting MCR allow reviewers to freely write messages to the author (and other reviewers), and frequently, these comments are superficial or do not clearly identify defects or relevant issues for the proposed change and are thus of questionable usefulness.

% (e.g. coding styles, documentation, process workflow, etc.)

For example, a comment may be related to something outside the scope of the proposed change, perhaps personal issues or inter-personal communication (e.g. ``Keep up the good work!").
Microsoft developers reported that the reviewers often only focus on minor logic errors rather than discussing deeper design\cite{Bacchelli2013a} issues.
Our observations of the Qt project also correspond to this finding.
We found some comments are superficial and unhelpful to the proposed changes.
For example, the superficial and unconfident comment shown in Fig. \ref{fig:example}(a) is indeed within the scope of the proposed change yet provides little useful information,
while the comment in Fig. \ref{fig:example}(b) about using the version control system (in this case Git) is clearly out of scope and not directly useful for the proposed change.

### 2014-07-27 sections/methods.tex
lots of change to the paper text.

% !TEX root = ../paper.tex

@@

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

>>>>

% !TEX root = ../paper.tex
%%
%%    THIS FILE IS NOT USED!
%%
%%    The Methods section has been merged with the Results section, now titled "Case Study."
%%

@@

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this project, we used the review history before June 13\textsuperscript{th}, 2012, which has 6,605 changes and 72,484 comments in its Gerrit code review system.

### 2014-07-27 sections/results.tex
lots of change to the paper text.

\section{Case Study}
%\pick{I'm exhausted...sorry. My writing here is pretty bad, hope you understand what I'm trying to say :)}

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject \texttt{qtbase} project. From this project, we used the review history from \TODO{Month-Year} to \TODO{Month-Year} which has \TODO{XX} reviews and \TODO{XX} comments.

\subsection{Data Preparation}
We used commit messages and comments in the dataset. Before classifying the usefulness of comments, we first processed the commit message and comments as follows:

\subsubsection{Automatically generated messages removal}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and the integration system to record activities. For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition. In practice they are not considered in code review. They are easily determined as useless by our method and would artificially improve our classification performance. We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.

>>>>

\section{Case Study}

Our case study used the Qt project review history from the Gerrit code review tool provided by Hamasaki et. al. \cite{Hamasaki2013}. Qt project is a large open source project composed of numerous small subsystems. We selected the most active subproject, which is called \texttt{qtbase}.
From this subproject, we used the review history before June 13\textsuperscript{th}, 2012, which contains 6,605 changes and 72,484 comments.

\subsection{Data Preparation}
We used the commit messages and comments in the dataset.
Before classifying the usefulness of comments, we first processed the commit message and comments as follows:

\subsubsection{Removal of automatically generated messages}
In Gerrit, the comments are composed of comment messages from reviewers and automated messages. These automatic messages are generated by Gerrit and the integration system to record activities. For example, \textit{'Upload patch set 1.'}, \textit{'Change has been successfully cherry-picked to the staging branch as ...'}. Since these messages are generally recored keeping, they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition. In practice they are not considered in code review. They are easily determined as useless by our method and would artificially improve our classification performance. We identified these automatic messages using regular expressions and selecting frequently appeared patterns of messages.
